\documentclass[a4 paper]{article}
% Set target color model to RGB
\usepackage[inner=2.0cm,outer=2.0cm,top=2.5cm,bottom=2.5cm]{geometry}
\usepackage{setspace}
\usepackage[rgb]{xcolor}
\usepackage{verbatim}
\usepackage{subcaption}
\usepackage{amsgen,amsmath,amstext,amsbsy,amsopn,tikz,amssymb,tkz-linknodes}
\usepackage{fancyhdr}
\usepackage[colorlinks=true, urlcolor=blue,  linkcolor=blue, citecolor=blue]{hyperref}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{rotating}
%\usetikzlibrary{through,backgrounds}
\hypersetup{%
pdfauthor={Ashudeep Singh},%
pdftitle={Homework},%
pdfkeywords={Tikz,latex,bootstrap,uncertaintes},%
pdfcreator={PDFLaTeX},%
pdfproducer={PDFLaTeX},%
}
%\usetikzlibrary{shadows}
% \usepackage[francais]{babel}
\usepackage{booktabs}
\input{macros.tex}


\begin{document}
\homework{Assignment 1}{Due: 02.04.2020 23:55}{Dr. Sergey Kosov}{Yuhou Zhou}
\textbf{Course Policy}: Read all the instructions below carefully before you start working on the assignment, and before you make a submission.
\begin{itemize}
    \item The homework assignments are for practice purpose. The grade from your homework will not affect your final grade of the course.
    \item Please submit your answer sheet, either by a scanned copy or a typeset PDF file, to Moodle before the deadline.
    \item No late submission is accepted.
    \item You can do this assignment in groups of 2. Please submit no more than one submission per group.
\end{itemize}

\problem{1: Factorization of joint distributions}{2.5+2.5=5}
Here we use the standard shorthand notation $P(x,y)$ for $P(X=x, Y=y)$, $P(x|y)$ for $P(X=x | Y=y)$, etc. Prove the following \textit{factorization formula}

\subproblem{a} $P(x, y, z) = P(x)P(y|x)P(z|x,y)$,

\subproblem{b} $P(u|v_1,\dots, v_n) = P(u, v_1,\dots, v_n) / P(v_1, \dots, v_n)$.\\

Note: in statistics and machine learning in general, factorizing joint distributions into products of simpler distributions is a super common strategy.

% \newpage

\problem{2: Expectation, Variance, and Covariance}{2.5+2.5+2.5+2.5+5+5=20}
\subproblem{a} Use $var[f(x)]=\mathbb{E}[(f(x)-\mathbb{E}[f(x)])^2]$ show that $var[f(x)]$ satisfies $var[f(x)]=\mathbb{E}[f(x)^2] - \mathbb{E}[f(x)]^2$.

\subproblem{b} Show that if two variables $x$ and $y$ are independent, then their covariance is zero.

\subproblem{c} Suppose that the two variables $x$ and $z$ are statistically independent. Show that the mean and variance of their satisfies

\begin{align*}
    \mathbb{E}[x+z] &= \mathbb{E}[x]+\mathbb{E}[z]\\
    var[x+z] &= var[x]+var[z]
\end{align*}

\subproblem{d} Give a derivation for the formula $Cov(X,Y)=\mathbb{E}[XY]-\mathbb{E}[X]\mathbb{E}[Y].$

\subproblem{e} Prove that the mean minimizes the quadratic loss, that is, for a random variable $X$ with values in $\mathbb{R}$,

\begin{equation*}
    \mathbb{E}[X]=argmin_{x \in \mathbb{R}} (\mathbb{E}[(x-X)^2])
\end{equation*}
Note: $argmin$ refers to the inputs, or arguments, at which the function outputs are as small as possible. e.g. $argmin_x(2x^2+4x-8)=-1$

\subproblem{f} Show that for two random variables $X, Y$ with values in $\mathbb{R}$, it holds that $-1\leq Corr(X,Y) \leq 1$. (Assuming that both RVs don't have zero standard deviation and that their joint distribution is characterized by a p.d.f. $f(x,y)$). You may use the following fact (a special case of the so-called \textit{Cauchy-Schwarz inequality}):
\begin{equation*}
    (\int_{\mathbb{R}^2} xy f(x,y) d(x,y) )^2 \leq \int_{\mathbb{R}^2} x^2 f(x,y) d(x,y) \cdot \int_{\mathbb{R}^2} y^2 f(x,y) d(x,y)
\end{equation*}
where $f$ is a p.d.f. on $\mathbb{R}^2$.

\end{document} 
